---
title: "week 2 test"
author: "ashy"
date: "10 November 2017"
output: html_document
---
=============================================

## Week 2 test
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



Loading the data set
We have many NA's in out "steps" column
```{r}
Week2 <- read.csv("C:\\Ashy\\Ashy\\cousera\\Reproducible research\\week 2\\activity.csv")

summary(Week2)

table(is.na(Week2$steps))

str(Week2)
```

What is mean total number of steps taken per day?

For this part of the assignment, you can ignore the missing values in the dataset.

Calculate the total number of steps taken per day
#Week2$steps[is.na(Week2$steps)]  <- 0 #replacing the NA's with Zero

```{r total number of steps per day}

steps <- aggregate(Week2$steps, by = list(Date = Week2$date), FUN = sum)

names(steps)[names(steps) == "x"] <- "Total"
temp <- as.Date(steps$Date, "%Y-%m-%d")
steps$Date <- format(temp, format = "%m-%d")
head(steps)

```

Make a histogram of the total number of steps taken each day.

```{r}
with(steps,hist(Total))

```


Calculate and report the mean and median of the total number of steps taken per day
```{r mean}
mean(steps$Total,na.rm = TRUE)


median(steps$Total,na.rm = TRUE)

```

What is the average daily activity pattern?
Make a time series plot (i.e. type = "l") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis)
```{r}

library(ggplot2)

Five_Min <- aggregate(steps ~ interval, data = Week2, FUN =mean)

TimeSeries <- ggplot(data = Five_Min, aes(x = interval, y = steps)) + 
    geom_line() +
    xlab("Time Intervals") + 
    ylab("Total Number of Steps") +
    ggtitle("Avg. steps")

print(TimeSeries)


```
Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?

```{r}
Five_Min[which(Five_Min$steps == max(Five_Min$steps)),]

```


Imputing missing values
Calculate and report the total number of missing values in the dataset (i.e. the total number of rows with NAs)
```{r}
sapply(X = Week2, FUN = function(x) sum(is.na(x)))

```

Devise a strategy for filling in all of the missing values in the dataset. The strategy does not need to be sophisticated. For example, you could use the mean/median for that day, or the mean for that 5-minute interval, etc

Create a new dataset that is equal to the original dataset but with the missing data filled in

```{r}

table(is.na(Week2$steps))
table(is.na(Week2$date))
table(is.na(Week2$interval))

Week2$steps[is.na(Week2$steps)] <- mean(Week2$steps,na.rm = TRUE)
table(is.na(Week2$steps))
table(is.na(Week2))

```


